---
title: "data preperation"
output: html_document
author: Itay Vjn Rayn
editor: Dvora Low Ramati
---



```{r}
library(tidyverse)
library("raster")

```



functions to convert the data from raw data to data


  1. swap.plus: 
    different sizes in the raw data are writen it that form: 2 M+1 L+ which mean: 2 boxes size Medium and 1 box size Large.
    replace + to _
    
   2. different_sizes: split words with "_" between them.
      that split 1 catch with 2 different sizes, convert them to 2 strings.
      
  ?  3. split_let_from_num: 
        split character with space. from "0.5 B" to "0.5" "B". 
        work in the loop, because need to activate on character, on single cell, can't use with whole list
        "term" is the name of 1 cell in the list in the loop in function 4
    
      4. proccesing:
        take the data, convert cell to character, call to the 1&2 functions,
        call function 3, and seperate the cells to columns of "Kg", and sizes [box_b, box_s...ind_b, ind_s...].
        The column "Ind kg" is the number of kg, when the number of fishes is in "Ind_no_size"
        Example: "2 Ind 5 Kg" will be data$ind_no_size=2, and data$ind_Kg=5
        

```{r}
#1.
  swap.plus<-function(cell){
  return(gsub("\\+", "_", cell))
}

#2.
  differrnt_sizes<-function(cell){
  return(strsplit(cell,"_"))
}

#3.
  split_let_from_num<-function(term){
  return(strsplit(term," "))
}

  
#4.
  processing<-function(cell,species_template){
  cell<-as.character(cell)
  cell<-swap.plus(cell)
  cell<-differrnt_sizes(cell)


  for(i in 1:length(cell[[1]])){
    term<-cell[[1]][i]
    term<-split_let_from_num(term)
    num<-as.numeric(term[[1]][1])

  #if length==1, it just number of boxes     
    if(length(term[[1]])==1){
      species_template$box_no_size<-num
    }#end if
    
  #if length==2, it's could be number+kg, number+size or number+individuals(Ind)
    if(length(term[[1]])==2){
      sizeA<-term[[1]][2]
      if(sizeA=="Ind"){
        species_template$ind_no_size<-num
      }#end if(sizeA) 
      else{
        if(sizeA=="Kg"){
          species_template$kg_no_size<-num
        }#end if(sizeA)
        else{
          if(sizeA=="B"){
            species_template$box_b<-num 
          }#end if(sizeA)
          if(sizeA=="S"){
            species_template$box_s<-num 
          }#end if sizeA
          if(sizeA=="M"){
            species_template$box_m<-num 
          }#end if(sizeA)
          if(sizeA=="L"){
            species_template$box_l<-num 
          }#end if(sizeA)
        }#end else
      }#end esle
    }#end if(lenghe...)
    
    
   #if length==3, it could be number+kg+size or number+individuals+size, number+size+another number
    #[1 box with size and one without]
    if(length(term[[1]])==3){
      sizeA<-term[[1]][2]
      sizeB<-term[[1]][3]
      if(sizeA=="Ind"){
        if(sizeB=="B"){
          species_template$ind_b<-num 
        }#end if(sizeB)
        if(sizeB=="S"){
          species_template$ind_s<-num 
        }#end if(sizeB)
        if(sizeB=="M"){
          species_template$ind_m<-num 
        }#end if(sizeB)
        if(sizeB=="L"){
          species_template$ind_l<-num 
        }#end if(sizeB)
      }#end if(sizeA)
      else{
        if(sizeA=="Kg"){
          if(sizeB=="B"){
            species_template$kg_b<-num 
          }#end if(sizeB)
          if(sizeB=="S"){
            species_template$kg_s<-num 
          }#end if(sizeB)
          if(sizeB=="M"){
            species_template$kg_m<-num 
          }#end if(sizeB)
          if(sizeB=="L"){
            species_template$kg_l<-num 
          }#end if(sizeB)
        }#end if(sizeA)
      
         if(sizeA=="B"){
            species_template$box_b<-num
            species_template$box_no_size = sizeB
          }#end if(sizeA)
          if(sizeA=="S"){
            species_template$box_s<-num 
            species_template$box_no_size = sizeB
          }#end if sizeA
          if(sizeA=="M"){
            species_template$box_m<-num
            species_template$box_no_size = sizeB
          }#end if(sizeA)
          if(sizeA=="L"){
            species_template$box_l<-num
            species_template$box_no_size = sizeB
            }#end if sezeA
        
      }#end else
    }#end if(length...)
     
    
  #if length==4, it could be number+ind+number+kg or num+size+num+another size [2 different sizes in boxes]
    if(length(term[[1]])==4){
      sizeA = term[[1]][2]
      sizeB = term[[1]][4]
      num2 <-as.numeric(term[[1]][3])
      
       if(sizeA=="Ind"){
          species_template$ind_no_size<-num
          species_template$ind_kg=num2
      }#end if(sizeA)
      
      else{
       
        if(sizeA=="B"){
            species_template$box_b<-num 
          }#end if(sizeA)
          if(sizeA=="S"){
            species_template$box_s<-num 
          }#end if sizeA
          if(sizeA=="M"){
            species_template$box_m<-num 
          }#end if(sizeA)
          if(sizeA=="L"){
            species_template$box_l<-num 
          }#end if(sizeA) 
        
        
         if(sizeB=="B"){
            species_template$box_b<-num2 
          }#end if(sizeB)
          if(sizeB=="S"){
            species_template$box_s<-num2 
          }#end if sizeB
          if(sizeB=="M"){
            species_template$box_m<-num2 
          }#end if(sizeB)
          if(sizeB=="L"){
            species_template$box_l<-num2 
          }#end if(sizeB)
        
      }#end else
    }#end if (length==4)
    
  #if length==6 it is 3 sizes of boxes: num+size+num+size+num+size
    if(length(term[[1]])==6){
      sizeA = term[[1]][2]
      sizeB = term[[1]][4]
      sizeC=term[[1]][6]
      num2 <-as.numeric(term[[1]][3])
      num3 = as.numeric(term[[1]][5])
       
        if(sizeA=="B"){
            species_template$box_b<-num 
          }#end if(sizeA)
          if(sizeA=="S"){
            species_template$box_s<-num 
          }#end if sizeA
          if(sizeA=="M"){
            species_template$box_m<-num 
          }#end if(sizeA)
          if(sizeA=="L"){
            species_template$box_l<-num 
          }#end if(sizeA) 
        
      
         if(sizeB=="B"){
            species_template$box_b<-num2 
          }#end if(sizeB)
          if(sizeB=="S"){
            species_template$box_s<-num2 
          }#end if sizeB
          if(sizeB=="M"){
            species_template$box_m<-num2 
          }#end if(sizeB)
          if(sizeB=="L"){
            species_template$box_l<-num2 
          }#end if(sizeB)
        
      
       if(sizeC=="B"){
            species_template$box_b<-num3 
          }#end if(sizeC)
          if(sizeC=="S"){
            species_template$box_s<-num3 
          }#end if sizeC
          if(sizeC=="M"){
            species_template$box_m<-num3 
          }#end if(sizeC)
          if(sizeC=="L"){
            species_template$box_l<-num3 
          }#end if(sizeC)
    
    }#end if (length==6)    
    
  }#end for
  
  return(species_template)
}#end function




```

  
  Creat empty vectors, requeried for the functions above, will use as columns in the new data
```{r}
species<-c(NA)
box_no_size<-c(NA)
box_b<-c(NA)
box_s<-c(NA)
box_m<-c(NA)
box_l<-c(NA)
ind_no_size<-c(NA)
ind_b<-c(NA)
ind_s<-c(NA)
ind_m<-c(NA)
ind_l<-c(NA)
ind_kg = c(NA)
kg_no_size<-c(NA)
kg_b<-c(NA)
kg_s<-c(NA)
kg_m<-c(NA)
kg_l<-c(NA)

```

uploud the data, and adding draging time column
```{r}
#upload the data
raw_data <- read.csv(file="data/all_data_2013_2018.csv", stringsAsFactors=FALSE)
raw_data[raw_data==""]<-NA

   
#adding draging time to raw data
  
  Draging_time<-rep(NA,length(raw_data$Net))
  for(i in 1:length(raw_data$Net)){
    end<-as.numeric(raw_data$End_Time_hh[i])+as.numeric(raw_data$End_Time_mm[i])/60
    start<-as.numeric(raw_data$Start_Time_hh[i])+as.numeric(raw_data$Start_Time_mm[i])/60
    if(is.na(start)| is.na(end)){
      
    }else{
      if(start>end){
        Draging_time[i]<-24-start+end
      }else{
        Draging_time[i]<-end-start
      }
    }
    
  }
raw_data=cbind(raw_data,Draging_time)


```

Order the data:
 Create a net index from the net number, day, month, year - to prevent problems from the defferent raw data files.
 seperate the name of the site from the direction. Ashdod N become to:
 data$site="Ashdod", data$direction=N

 save the data

```{r}
#convert to tibble, and cerate net index from the Net column and the year
data=as_tibble(raw_data)
data=mutate(data, Net_index=paste(data$Net, data$Day.XX., data$Month.XX., data$Year.XXXX.,sep = "_"))

#erase empty column - 
#!!!!-----CUATION - CHECK IF IN iTAY DATA THIS COLUMN IMPORTANT!!!!!!!---
data =data %>% dplyr::select(everything(),-Fishing_field_text) 


#Seperate site and direction:
#create site vectors
site=data$Fishing_field
Direction=rep(NA,length =length(site))

direc_vec=c("N","W","E","S")

#seperate the strings
site=strsplit(site," ")

  for (i in 1:length(site)) {

    #if the is to direction and one place: Ashdod N E
    if ((site[[i]][2] %in% direc_vec)&(site[[i]][3] %in% direc_vec)) {
      Direction[i]=paste(site[[i]][2],site[[i]][3],sep = " ")    
      site[[i]][2]="_"
      site[[i]][3]="_"
      site[i]=paste(site[[i]][1],site[[i]][2],site[[i]][3])
      site[i]=gsub("\\ _ _","",site[i])
          
    }#end if
  
    #just one site and one direction: Asdod N
    if (site[[i]][2] %in% direc_vec) {Direction[i]=site[[i]][2]
                                   site[[i]][2]="_"
                                   site[i]=paste(site[[i]][1],site[[i]][2])
                                   site[i]=gsub("\\ _","",site[i])
                                   }#end if
    
    #site with 2 words and 1 direction: Bat Yam N
    if (site[[i]][3] %in% direc_vec)  {Direction[i]=site[[i]][3]
                                    site[[i]][3]="_"
                                   site[i]=paste(site[[i]][1], site[[i]][2],site[[i]][3])
                                   site[i]=gsub("\\ _","",site[i])
                                  }#end if
  
   #just site with 1 word
    if (is.na(site[[i]][2])==FALSE ){
       site[i]=paste(site[[i]][1],site[[i]][2],sep = " ")
    }#end if
  
}#end for


site=as.vector(unlist(site))
data=cbind(data,site,Direction)


write.csv(data,file = "prosseced data/new_data_prosseced_raw.csv")

data = read.csv(file ="prosseced data/new_data_prosseced_raw.csv")


```



In the raw data, there is information about number of catch, size, and KG or Box in one cell, and here its seperated.
This chunk is oredering the data to one line for any single catch, with all the information about the net, and also sepereate columns for catches with size reported, and for Kg catches.


```{r}

temp_data<-c()

#create vector contain the species names
 species_vector =   colnames(dplyr :: select(data,Anshubi:Aras,-(Many.Nasralas),-(Comments),-(Missing),-(Very_weak)))


nets<-c(1:length(data[,1]))
#nets<-c(1:300)

night_drag.place<-which(colnames(data)=="night_drag_prawn")


#loop get over any row in the data an call to the "processing" function for sepertate and sort the catch strings
#[more explanation above, in the function chunk]

#run on any row
  for(i in nets){

  #create empty data frame with the required columns
    net_template<-cbind(data[1:night_drag.place][i,],"Many.Nasralas"= data$Many.Nasralas[i], "Very_weak"=data$Very_weak[i], "Missing"= data$Missing[i], "Comments"= data$Comments[i], "Draging_time"=data$Draging_time[i], "Net_index"=data$Net_index[i],"Site"=data$site[i],"Direction"=data$Direction[i], species, box_no_size, box_b, box_s, box_m, box_l, ind_no_size, ind_b, ind_s, ind_m, ind_l, ind_kg, kg_no_size, kg_b, kg_s, kg_m,kg_l) # net data might have more than 1 rows 
 
  net<-c()
  
  # run on any species
  for (j in species_vector){
    if(is.na(data[i,j])==F){ #species cell NA or not
      species_template<-net_template
      species_template$species<-colnames(data[j])# species data might have more than 1 rows
      
  #There is data in the format: "1 Ind 2 Kg 1 Ind 5 Kg", in these case, split the data to two rows, the original
  #row, just with the first fish ("1 Ind 2 Kg"), and another row, with the same net information, but just with
  #the second fish in the catch part ("1 Ind 5 Kg") [other species received NA]
      
      #seperate the cell strings
      cell_length=data[i,j]
      cell_length=gsub("\\+ ","",cell_length)
      cell_length=gsub("\\+"," ",cell_length)
      cell_length=as.character(cell_length)
      cell_length=strsplit(cell_length," ")
    
      #If it have 8 strings, split to 2 rows:
      if (length(cell_length[[1]])==8)
      {
        cell_length_A=paste(cell_length[[1]][1],cell_length[[1]][2],cell_length[[1]][3],cell_length[[1]][4])
        cell_length_B=paste(cell_length[[1]][5],cell_length[[1]][6],cell_length[[1]][7],cell_length[[1]][8])
       split_row=data[i,]
       split_row[20:81]=NA
         split_row[j]= cell_length_B
        data[i,j]=cell_length_A
        data=rbind(data,split_row)
      }#end if
      
      #call to the process function - order the data to seperate columns
      species_data<-processing(data[i,j],species_template)
      net<-rbind(net,species_data)
     
    }#end if(is.na)
  }# end j loop
  temp<-rbind(temp_data,net)
  temp_data<-temp
}#end i loop




```





 
Convert the data to Kg box is 10 Kg.
Individuals of Lokus, Musar and Sultan Mix with size, I convert to Kg up to the estimate of Levi, the fisherman

```{r}
  kg_data=temp_data
  
  for (i in 1:length(kg_data$Net)) {
    
    if(is.na(kg_data$box_no_size[i])==FALSE)
    {
      kg_data$kg_no_size[i]=(kg_data$box_no_size[i]*10)
      kg_data$box_no_size[i]=NA
    }#end if
    
    if(is.na(kg_data$box_b[i])==FALSE)
    {
      kg_data$kg_b[i]=(kg_data$box_b[i]*10)
      kg_data$box_b[i]=NA
    }#end if
    
     if(is.na(kg_data$box_s[i])==FALSE)
    {
      kg_data$kg_s[i]=(kg_data$box_s[i]*10)
      kg_data$box_s[i]=NA
    }#end if
    
    
     if(is.na(kg_data$box_m[i])==FALSE)
    {
      kg_data$kg_m[i]=(kg_data$box_m[i]*10)
      kg_data$box_m[i]=NA
    }#end if
    
     if(is.na(kg_data$box_l[i])==FALSE)
    {
      kg_data$kg_l[i]=(kg_data$box_l[i]*10)
      kg_data$box_l[i]=NA
    }#end if
    
    #if there are ind with no size, but with kg, the Kg is number of individuals*individuals kg. 
    if(is.na(kg_data$ind_no_size[i])==FALSE)
    { if(is.na(kg_data$ind_kg[i])==FALSE)
        { 
        kg_data$kg_no_size[i]=(kg_data$ind_no_size[i]*kg_data$ind_kg[i])
        kg_data$ind_no_size[i]=NA
        kg_data$ind_kg[i]=NA
        }#end if
      
    }#end if
   
    #there are smal individuals of Lokus
    if(is.na(kg_data$ind_s[i])==FALSE)
    {
      if (kg_data$species[i]=="Lokus")
      {
        kg_data$kg_no_size[i]=2
        kg_data$ind_s[i]=NA
      }#end if
    }#end if
    
    #there are meduim individuals of Lokus
    if(is.na(kg_data$ind_m[i])==FALSE)
    {
      if (kg_data$species[i]=="Lokus")
      {
        kg_data$kg_no_size[i]=5
        kg_data$ind_m[i]=NA
      }#end if
    }#end if
    
    #there are large individuals of Lokus, Musar, and Soltan mix
     if(is.na(kg_data$ind_l[i])==FALSE)
    {
      if (kg_data$species[i]=="Lokus")
      {
        kg_data$kg_no_size[i]=12.5
        kg_data$ind_l[i]=NA
      }#end if
       
       if (kg_data$species[i]=="Musar")
      {
        kg_data$kg_no_size[i]=10
        kg_data$ind_l[i]=NA
      }#end if
       
         if (kg_data$species[i]=="Soltan_Mix")
      {
        kg_data$kg_no_size[i]=0.2
        kg_data$ind_l[i]=NA
      }#end if
    }#end if
    
  }#end for



```



 swich to other data - new_data.
  if we want to save the information about size, it's required to split any row with 2 [or 3] different sizes, and to make it 2 rows.

 replace NA to 0 in the catch [and convert to tibble]

 
```{r}

#switch to "new_data" because I will erase the sizes information
new_data=kg_data

#replace NA to zero, just in the catch part, in very clumsy way =(
temp_data = new_data %>% dplyr:: select(box_no_size:kg_l)
temp_data[is.na(temp_data)]=0
new_data=dplyr:: select(new_data,-(box_no_size:kg_l))
new_data=cbind(new_data,temp_data)
new_data=dplyr:: select(new_data,Net,Net_index,everything())

#sum the  kg columns 
new_data$kg_s=as.numeric(new_data$kg_s)
new_data= new_data %>% mutate (Kg= kg_b+kg_l+kg_m+kg_no_size+kg_s)

#erase the unnessesary columns  - now the catch is just in "Amount" and "Unit", with mo size
new_data =new_data %>% dplyr::select(everything(),-(box_no_size:kg_l))
write.csv(new_data,file = "prosseced data/new_data_one_kg_col.csv")
long_data = read.csv("prosseced data/new_data_one_kg_col.csv")


```

Sum the amount [Kg] of duplicates rows
Convert the data to wide format - with zeros instead of NA


```{r}
 

grouping <- colnames(long_data)[2:30]

wide_data = long_data %>%
   dplyr:: select(everything(),-X.1) %>%
  group_by(.dots = grouping) %>% summarize(Kg = sum(Kg)) %>%
  spread(key = species,value = Kg,fill = 0)


```


names of species - from common name to code
first we need to put the sceinticifcs names and code from Itay, side by side neer our species common name, to comper
```{r}
#uploud Itay sceintific names [old data]
sceintific_names=read.csv("data/species_scientific_name.csv")
#create and join empty row, to make the datas equal
emepty_row=rep(NA,13)
sceintific_names = rbind(sceintific_names, emepty_row)
sceintific_names = dplyr::select(sceintific_names, Sp_code, Common_name, Sceintific_name=scintific_name)
#sort by A-Z of the common name
sceintific_names = sceintific_names[order(sceintific_names$Common_name),]
#sort the vector from new data and join
species_vector_sort=species_vector[order(species_vector)]



#arase from the data empty columns.
#The Jelly fish had just 5 records, so I chose to arease it [I think most of the time they not reported]
wide_data=wide_data %>% dplyr::select(everything(),-kg.Jelly_Fish, -kg.barbon_vadim,  -kg.Gerbid_new, -kg.Vest)
#cerate name vector
names_vector =   colnames(dplyr :: select(wide_data,kg.Anshubi:kg.Aras))
  
  #remove the Kg form the names
  for (i in 1:length(names_vector)) {
  names_vector[i] = gsub("kg.", "", names_vector[i] )  
  }
   
   
 #uploud an uplate of the scintific name - data with common names, origin, code, and scientific names - I joined to Itay names sum new species with new code
code_sceintific_names= read.csv(file="data/species_scientific_name_new_data.csv",stringsAsFactors=FALSE)

#order the names in the vector from the data=names vector, and in the sceintific names data
  code_sceintific_names=code_sceintific_names[order(code_sceintific_names$Common_name),]
  names_vector=names_vector[order(names_vector)]

  #join the vectors to ensute they equal
code_sceintific_names=cbind(code_sceintific_names,names_vector)

#replace the "kg" in the colnames of the species
  library(stringr)
     wide_data = wide_data %>% rename_at(vars(starts_with("kg.")), funs(str_replace(., "kg.", "")))
 
 #order the data
  wide_data=wide_data[,order(colnames(wide_data))]
  wide_data= wide_data %>% dplyr::select(net_index,everything())

  #replace the colnames from common names to codes in cumsy way...
  code_vector=code_sceintific_names$Sp_code
  for (i in 1:length(names_vector))
  {
    names(wide_data)[i+1]=code_vector[i]
  }#end for

```





```{r}
#import the raster file, subset and manage projection

#I run thes rows in regular R script, not here in Rmarkdown. has to be OK in git!
library(rgdal)
med_rast1=raster("map_med.txt")

med_rast1[med_rast1<(-300)]<-NA
med_rast1[med_rast1>0]<-NA
crs(med_rast1) <- "+proj=utm +zone=36"
med_rast1= projectRaster(med_rast1, crs = "+proj=longlat")


#import data frame with shore locations
location_data <- read.csv("data/locations_lat_on_shore.csv")
colnames(location_data)=c("Site","Lat_shore","Lon_shore","Perpendicular")

#merge the data and order the columns
loc_data=merge(wide_data,location_data)
loc_data = dplyr::select(loc_data, Net:Net_index, Start_Time_hh:Draging_time, Site, Direction, Lat_shore:Perpendicular,Adom:Vest)


#phatom to meters
loc_data$Depth_m=1.8*loc_data$Depth
#nautical miles to Km
loc_data$Distance_to_Shore = as.numeric(loc_data$Distance_to_Shore)
loc_data$Distance_from_shore_km=1.8*loc_data$Distance_to_Shore

#next we will work with net which location with lat and lon (the lat and lon are on the shore in front of the fishing location)
#first we will create 3 new column for indexing the type of data for each net
#for nets with depth
loc_data$depth_specifyed=rep(NA,nrow(loc_data))
loc_data[!is.na(loc_data$Depth_m),"Depth_specifyed"]=T
#for nets with distance
loc_data$distance_specifyed=rep(NA,nrow(loc_data))
loc_data[!is.na(loc_data$Distance_from_shore_km),"Distance_specifyed"]=T
#for nets with starting position
loc_data$Location_specifyed=rep(NA,nrow(loc_data))
loc_data[!is.na(loc_data$Site),"Location_specifyed"]=T

#For net with location and depth we can use new location by crossing the latitude and the depth
#building a function for calculating the depth in pront of each location
location_depth_based=function(Lon,Lat,Perpendicular,target_depth){
  #first is a vector of distances from the starting location to choose from
  distances=seq(0,28000,100)
  loc_dt=data.frame()#list of data frames for each location. each data frame with 3 columns: lat,lon,depth
  start_position=SpatialPoints(data.frame(Lon,Lat), proj4string=CRS("+proj=longlat"))#create spetial object
  #next is the depwth in each of the distances
  for (d in distances){
    loc=data.frame(destPoint(start_position,Perpendicular,d))
    loc_c=SpatialPoints(loc, proj4string=CRS("+proj=longlat"))
    loc_UTM=spTransform(loc_c,CRS("+proj=utm +zone=36"))#transform fom degrees to UTM
    loc_DEPTH=extract(med_rast1, loc_c)#this will give the depths of the individuals
    loc$depth=loc_DEPTH
    loc_dt=rbind(loc_dt,loc)#adding to the data frmae of all points in the location
  }
  if (nrow(loc_dt[complete.cases(loc_dt),])==0){
    location=data.frame(lon_final=NA,lat_final=NA,Depth_diff=NA)}else{
      target_location=which(abs(loc_dt$depth-(-1*target_depth))==min(abs(loc_dt$depth-(-1*target_depth)),na.rm = T))
      print(min(abs(loc_dt$depth-(-1*target_depth)),na.rm = T))
      if (min(abs(loc_dt$depth-(-1*target_depth)),na.rm = T)>10){
        location=data.frame(lon_final=NA,lat_final=NA,Depth_diff=min(abs(loc_dt$depth-(-1*target_depth)),na.rm = T))
      }else{
        target_location=some(target_location,1)
        location=data.frame(lon_final=loc_dt[target_location,"lon"],lat_final=loc_dt[target_location,"lat"],Depth_diff=min(abs(loc_dt$depth-(-1*target_depth)),na.rm = T))}
    }
  return(location)
}
library(tidyr)
detach("package:tidyr", unload=TRUE)
#applying the function
loc_data$Lon_final=rep(NA,nrow(loc_data))
loc_data$Lat_final=rep(NA,nrow(loc_data))
loc_data$Depth_diff=rep(NA,nrow(loc_data))
#nrow(loc_data)
nrow(loc_data)
for (r in 1:nrow(loc_data)){
  print(r)
  row_c=loc_data[r,]
  if (!is.na(row_c$lat_shore) & !is.na(row_c$Depth_m)){
    final_loc=location_depth_based(loc_data[r,"Lon_shore"],loc_data[r,"Lat_shore"],loc_data[r,"Perpendicular"],loc_data[r,"Depth_m"])
    loc_data[r,"Lon_final"]=final_loc[1,"lon_final"]
    loc_data[r,"Lat_final"]=final_loc[1,"lat_final"]
    loc_data[r,"Depth_diff"]=final_loc[1,"Depth_diff"]
  }else{}
}




#next find location by distance to shore
location_distance_based=function(Lon,Lat,Perpendicular,distance){
  #first is a vector of distances from the starting location to choose from
  dist_m=distance*1000
  start_position=SpatialPoints(data.frame(Lon,Lat), proj4string=CRS("+proj=longlat"))#create spetial object
  position=destPoint(start_position,Perpendicular,dist_m)
  location=data.frame(lon_final=position[1,"lon"],lat_final=position[1,"lat"])
  return(location)}
#run on data
for (r in 1:nrow(loc_data)){
  print(r)
  row_c=loc_data[r,]
  if (!is.na(row_c$lat_shore) & is.na(row_c$Depth_m) & !is.na(row_c$Distance_from_shore_km)){
    final_loc=location_distance_based(loc_data[r,"lon_shore"],loc_data[r,"lat_shore"],loc_data[r,"perpendicular"],loc_data[r,"Distance_from_shore_km"])
    loc_data[r,"Lon_final"]=final_loc[1,"lon_final"]
    loc_data[r,"Lat_final"]=final_loc[1,"lat_final"]
  }else{}
}

#Insert depth based on the location
loc_data$loc_DEPTH=extract(med_rast1, loc_data[,c("Lon_final","Lat_final")])
loc_data$loc_DEPTH=abs(loc_data$loc_DEPTH)
##Test if location based depth are good
#summary
summary(loc_data$loc_DEPTH)
#compare to nets with specified depth
depth_specified=subset(loc_data,depth_specifyed==T)
depth_specified$Depth_diff=depth_specified$loc_DEPTH-depth_specified$Depth_m
depth_check=data.frame(observed_depth=depth_specified$Depth_m,location_depth=depth_specified$loc_DEPTH,Depth_diff=depth_specified$Depth_m-depth_specified$loc_DEPTH)
summary(depth_check$Depth_diff)
plot(depth_specified$Depth_m,depth_specified$loc_DEPTH)


```




     



















-----------------------------
A code check for nets with no speceis except gamberi, fish, Kalamari and Box general
and replace the zeros to NA
I think it is unessesary for me
------:
#look for nets with only 'box_general'  
data_wide$exept_general=rowSums(subset(data_wide, select = -c(net_index,amount.Box_General)))#this line will add a column with the sum of all catchs except 'Box_GEneral'
data_wide$exept_general_gambari_kalamari=rowSums(subset(data_wide, select = -c(net_index,amount.Box_General,amount.Gambari,amount.Kalamari,amount.Fish)))#this line will add a column with the sum of all catchs except 'Box_General','Gambari' and 'Kalamari', 'Fish'

#return net indexs where there is box general and Gambari/Kalamari but no other amounts
t_drop=subset(data_wide,exept_general_gambari_kalamari==0)
net_indexes_to_na=unique(t_drop$net_index)

#replace the 0 to NA's
for (r in 1:nrow(zero_data)){
  print(r)
  row_inf=zero_data[r,]
  cond_net_index=row_inf$net_index %in% net_indexes_to_na
  cond_sp=row_inf$sp %in% c("Box_General","Gambari","Kalamari","Fish")
  if (cond_net_index==T & cond_sp==F){
    zero_data[r,"amount"]=NA
  }else{}
}
#For a single net- if there are specified species data we can assume that species which are not written wasn't present in the net.
#In that case for the same net the catch for these species will equal 0
#For nets with no specieis information we can no if a species was or wasn't in the catch
#use cast function from reshape2
add_sp_names=function(data_in){
sp_in_nets=cast(data_in, net_index ~ Sp_code,value="final_amount.x")
sp_in_nets[is.na(sp_in_nets)]=0
#net data
net_info_dt=data_in[!duplicated(data_in$net_index), ]
net_info_dt <- net_info_dt[, !(colnames(net_info_dt) %in% c("Sp_code","final_amount.x","species","box","size","unit","final_amount.y","box_numeric" ))]
#merge
full_data_zero_filled=merge(net_info_dt,sp_in_nets,by="net_index")
return(full_data_zero_filled)}

#apply on both data sets
Full_data_Kg_zeros=add_sp_names(Full_data_Kg)
Full_data_boxes_zeros=add_sp_names(Full_data_boxes)




#------ !!!!!!! CAUTION !!!!!! ------!!! not run !!!---------------------
#!!!!not nessecary after run agian the whole code - corect in the raw data!!!!!!!!!!!
wide_data$kg.Adom[1668]=0
wide_data$kg.Gambari[419] = wide_data$kg.Adom[419]
wide_data$kg.Adom[419]=0
#-----!!!!end of correct not to run in the future!!! ---------------

